\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-01-11 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added Christina Morency's section about poroelastic runs to the manual, and fixed a problem on the cover

\end{description}
If you use PML, the mesh elements that belong to the PML layers can
be acoustic or elastic, but not viscoelastic nor poroelastic. Then,
when defining your model, you should define these absorbing elements
as either acoustic or elastic. In you forget to do that, the code
will fix the problem by automatically converting the viscoelastic
or poroelastic PML elements to elastic. This means that strictly speaking
the PML layer will not be perfectly matched any more, since the physical
model will change from viscoelastic or poroelastic to elastic at the
entrance of the PML, but in practice this is sufficient and produces
only tiny / negligible spurious reflections.

>>>>

The present version of SPECFEM can handle fully saturated porous simulations, Christina Morency implemented Biot equation. 
But the code cannot calculate partially saturated cases in its state.
Christina Morency is presently working on a dual porosity, dual permeability formulation, type Pride and Berryman, for an other project, but it will not be available for some time.\\

The way we prescribe material property for porous material in SPECFEM3D is as follow:
We use a file name nummaterial\_poroelastic\_file, which is located in the directory MESH, the format is as follow:\\
 rhos rhof phi c kxx kxy kxz kyy kyz kzz Ks Kf Kfr etaf mufr\\
where\\ 
rho\_s = solid density\\
rho\_f = fluid density\\
phi = porosity\\
tort = tortuosity\\
kxx = xx component of permeability tensor\\
kxy = xy,yx components of permeability tensor\\
kyy = yy component of permeability tensor\\
kxz = xz,zx components of permeability tensor\\
kzz = zz component of permeability tensor\\
kappa\_s = solid bulk modulus\\
kappa\_f= fluid bulk modulus\\
kappa\_fr= frame bulk modulus\\
eta\_f = fluid viscosity\\
mu\_fr = frame shear modulus.\\

Using an external mesh (for instance coming from CUBIT/TRELIS), poroelastic materials have the ID number 3, while 1 is elastic, 2 is acoustic ? see the example in the package: examples/homogeneous\_poroelastic.

If you use PML, the mesh elements that belong to the PML layers can
be acoustic or elastic, but not viscoelastic nor poroelastic. Then,
when defining your model, you should define these absorbing elements
as either acoustic or elastic. In you forget to do that, the code
will fix the problem by automatically converting the viscoelastic
or poroelastic PML elements to elastic. This means that strictly speaking
the PML layer will not be perfectly matched any more, since the physical
model will change from viscoelastic or poroelastic to elastic at the
entrance of the PML, but in practice this is sufficient and produces
only tiny / negligible spurious reflections.
